Stats

### 2022-03-22 stats/analysis.Rmd
create clickDistInBalloons and symmetricPosition as overall variables. add age model in variation section, add age corrected retest model

```{r load_data}
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

```{r variation_hedge_preparateData}
variationHedgeInd <- vali %>% 
  filter(studyversion == "hedge") %>% 
  mutate(
    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
  ) %>% 
  group_by(sample, datacollection, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>%
  summarise(mean = mean(abs(clickDistFromTargetCenterX)/160, na.rm = TRUE))

@@

@@

@@

## Internal consistency
```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
}

hedge_intCon_data <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    # summarize bins, so that 9 + 10 = bin 5
    # bin = ceiling(as.numeric(targetPosition)/2)

    # summarize so that 1 + 10 = bin 5
    symmetricBin = case_when(targetPosition == "5" | targetPosition == "6" ~ 1, 
                             targetPosition == "4" | targetPosition == "7" ~ 2,
                             targetPosition == "3" | targetPosition == "8" ~ 3, 
                             targetPosition == "2" | targetPosition == "9" ~ 4,
                             targetPosition == "1" | targetPosition == "10"~ 5, 
                       )
  )

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_hedge_randomStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

@@

```{r splithalfr_hedge_adults}
# random split
splitscores_hedge_random_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_hedge_randomStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

@@

# random split
splitscores_box_random_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_box_randomStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE, 
)

@@

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE
)

@@

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

@@

```{r splithalfr_box_adults}
# random split
splitscores_box_random_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_box_randomStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE,
)

@@

# odd even split
splitscores_box_oddeven_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

@@

# first second testhalves split
splitscores_box_firstsecond_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

@@

```{r retest_hedge_data}
# take data of first reli day for internal consistency
hedge_retest <- reli %>% 
  filter(studyversion == "hedge") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```
```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

@@

>>>>

```{r load_data}
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli")),

    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
    # the smaller the value, the more central the position
    symmetricPosition = case_when(
                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1, 
                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3, 
                                  targetPosition == "2" | targetPosition == "9" ~ 4,
                                  targetPosition == "1" | targetPosition == "10" ~ 5, 
                       ),

    # distance between target and click in balloon widths (balloon width is 160 SVG units)
    clickDistInBalloons = clickDistInBalloons,
  )
```

@@

```{r variation_hedge_preparateData}
variationHedgeInd <- vali %>% 
  filter(studyversion == "hedge") %>% 
  mutate(
    ageInYearsExact = ifelse(sample == "kids", ageInMonths/12, 18), 
    ageInMonthsCentered = scale(ageInYearsExact, center = TRUE, scale = TRUE)[,1],
  ) %>% 
  group_by(sample, datacollection, ageInYears, ageInYearsExact, ageInMonthsCentered, subjID) %>%
  summarise(mean = mean(clickDistInBalloons, na.rm = TRUE))

@@

```{r age_hedge_model}
mDataAgeHedge <- vali %>% 
  filter(studyversion == "hedge" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)

mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeHedge,
                    family = lognormal(),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)
```

@@

```{r age_box_model}
# define data
mDataAgeBox <- vali %>% 
  filter(studyversion == "box" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, datacollection, symmetricPosition, targetPosition, correctBox)

mAgeBox <- brm(correctBox ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
                    data = mDataAgeBox,
                    family = bernoulli(link = "logit"),
                    warmup = 1000, 
                    iter   = 3000, 
                    chains = 4, 
                    inits  = "random",
                    cores  = 4)
```

@@

## Internal consistency
```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)

@@

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(clickDistInBalloons, na.rm = TRUE))
}

hedge_intCon_data <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1")

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_hedge_randomStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

```{r splithalfr_hedge_adults}
# random split
splitscores_hedge_random_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_hedge_randomStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
  replications = 10000,
  method = c("odd_even"),
)

@@

# random split
splitscores_box_random_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_box_randomStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE, 
)

@@

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE
)

@@

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

@@

```{r splithalfr_box_adults}
# random split
splitscores_box_random_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

@@

# random split with stratification by target position
splitscores_box_randomStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 10000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE,
)

@@

# odd even split
splitscores_box_oddeven_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("odd_even"),
)

@@

# odd even split with stratification by target position
splitscores_box_oddevenStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

@@

# first second testhalves split
splitscores_box_firstsecond_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 10000,
  method = c("first_second"),
)

@@

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 10000,
  method = c("odd_even"),
  careful = FALSE,
)

@@

```{r retest_hedge_data}
# take data of first reli day for internal consistency
hedge_retest <- reli %>% 
  filter(studyversion == "hedge") %>% 
  group_by(subjID, reliday, sample, ageInYears) %>% 
  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)

@@

# summary
psych::describeBy(box_retest, box_retest$sample)
```

```{r retest_box_kids}
box_retest_kids <- box_retest %>% 
  filter(sample == "kids") %>% 
  ggplot(., aes(x = mean_reliday1, y = mean_reliday2)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_point(aes(col = ageInYears), size = 0.7) + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d"), guide = "none") +
  geom_smooth(method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0, label.y = 1, aes(label = paste(..r.label..)), size = 3.5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = "Testday 1", y = "Testday 2")

@@

```{r retest_hedge_model}
# define data
mDataRetestHedge <- reli %>% 
  filter(studyversion == "hedge" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, reliday, clickDistInBalloons)

# run model
mRetestHedge <- brm(clickDistInBalloons ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestHedge, 
                              family = lognormal(), 
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)
```

```{r retest_box_model}
# define data
mDataRetestBox <- reli %>% 
  filter(studyversion == "box" & sample == "kids") %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age = scale(ageInMonths, center = TRUE, scale = TRUE)[,1], 
  ) %>% 
  select(subjID, age, reliday, correctBox)

# run model
mRetestBox <- brm(correctBox ~ age + (0 + reliday | subjID), 
                              data   = mDataRetestBox, 
                              family = bernoulli(link = "logit"),
                              warmup = 1000, 
                              iter   = 3000, 
                              chains = 4, 
                              inits  = "random",
                              cores  = 4)
```

@@

```{r save_model_output}
# mcor <- model_cor %>%
#     mutate(task = recode(task,
#                     `mutual_exclusivity` = "Mutual Exclusivity",
#                     `informativeness` = "Informativeness Inference (1)",
#                     `simple_inf` = "Informativeness Inference (2)",
#                     `preference` = "Speaker Preference",
#                     `novelty` = "Discourse Novelty",
#                     `card_sorting` = "Card Sorting",
#                     `discourse_continuity` = "Discourse Continuity",
#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
#                     `match_to_sample` = "Relational Match-to-sample"),
#            term = task, 
#            mcor = Estimate, 
#            mcor_lci = `l-95% CI`, 
#            mcor_uci = `u-95% CI`)%>%
#   select(study, term, task, mcor, mcor_lci, mcor_uci)

# saveRDS(mcor, "model_results.rds")
```
